---
title: "Econometría I: CORTE TRANSVERSAL"
subtitle: "<small>Alejandro Herrera Jiménez (U.C.B.)  Semestre I-2023</small>"
output: 
  revealjs::revealjs_presentation:
    theme: white
    highlight: pygments
    center: true    
    self_contained: false
    reveal_plugins: 
     # - search
      - zoom
      - notes
      - chalkboard
      - menu
    reveal_options:
      chalkboard:
        theme: chalkboard
        toggleNotesButton: true
      menu:
        numbers: true
      previewLinks: true  
---

# Horizontal Slide 1
<h3>The Lorenz Equations</h3>

$$y_i=\beta_0 + \beta_1 x_i + \varepsilon_i$$

\begin{aligned}
					  \dot{x} &amp; = \sigma(y-x) \\
					  \dot{y} &amp; = \rho x - y - xz \\
					  \dot{z} &amp; = -\beta z + xy
\end{aligned} 
					
## Vertical Slide 1

## Vertical Slide 2

# Horizontal Slide 2

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

<small>This sentence will appear smaller.</small>

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

